Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2020-06-05 paper/zigzag.tex
add zigzag -> zigzag geometry

\comment{We compare $E_\textrm{gap}(l_e)$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag and disorder both increase $E_\textrm{gap}$ through a similar mechanism.}
The right amount of disorder improves the Majorana properties~\cite{Haim2019} and scatters long trajectories in a similar fashion to the zigzag geometry cutting off long trajectories.
We simulate devices with disorder---parameterized by its mean free path $l_e$---and calculate $E_\textrm{gap}(l_e)$ for straight and zigzag devices at different phases and magnetic fields, see Fig.~\ref{fig:mfp_vs_gap}.
For the parameters we chose, at $\phi=0$ we observe that an optimal value of $l_e$ results in an enhancement that is at best equal to that of the zigzag device.
At $\phi=\pi$ we observe that zigzag outperforms disorder.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/mfp_vs_gap.pdf}
\caption{Comparison of the gap of zigzag devices (dashed lines) and straight devices (solid lines) as function of mean free path $l_e$.
\label{fig:mfp_vs_gap}}
\end{figure}

>>>>

\comment{We compare $E_\textrm{gap}(l_e)$ for zigzag and straight systems at $\phi=0$ and $\phi=\pi$; and confirm that the zigzag and disorder both increase $E_\textrm{gap}$ through a similar mechanism.}
The right amount of disorder improves the Majorana properties~\cite{Haim2019} and scatters long trajectories in a similar fashion to the zigzag geometry cutting off long trajectories.
We simulate devices with disorder---parameterized by its mean free path $l_e$---and calculate $E_\textrm{gap}(l_e)$ for straight and zigzag devices at different phases and magnetic fields, see Fig.~\ref{fig:mfp_vs_gap}.
For the parameters we chose, at $\phi=0$ we observe that an optimal value of $l_e$ results in an enhancement that is at best equal to that of the zigzag device.
At $\phi=\pi$ we observe that zigzag geometry outperforms disorder.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/mfp_vs_gap.pdf}
\caption{Comparison of the gap of zigzag devices (dashed lines) and straight devices (solid lines) as function of mean free path $l_e$.
Each $E_\textrm{gap}$ value is averaged over 40 disorder realizations and is calculated using a translationally invariant system where the unit-cell is $L_x=3z_x$, with $z_x=\SI{1300}{\nm}$.
\label{fig:mfp_vs_gap}}
\end{figure}
